The limits of self-commitment and private paternalism \\ Preliminary --comments welcome

### 2023-02-28 donde.tex
presentation

\subsection{Experimental Integrity}

\paragraph{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results. The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter.  If this occurred it would introduce a self-selection dimension which would still reflect the overall impact of a treatment for the lender's portfolio but would no longer deliver \textit{ceteris paribus} effects of treatments on the same individual borrower.  Narrative reports and the way the treatment was implemented make us believe that this is unlikely.\footnote{Potential clients did not know that different days could have different contracts. If they asked, appraisers said that whatever was offered on that day was the only available contract for an undetermined length of time. Anecdotally, appraisers told us that they did not think refusals differed across arms, and our enumerators informed us that potential clients rarely left the branch without pawning. Lender P also never complained to us that our different treatments were hurting sales.} If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms.  To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day. The \hl{first} row of Table \ref{attrition_table} shows there is no difference between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.\footnote{The Choice arm appears to have a somewhat larger number of borrowers than the Control arm (p-value=\hl{XXX}), but we cannot reject equality with the Forced Commitment arm (p-value=\hl{XXX}), or across all arms (p-value=\hl{XXX}).}  The second row makes the same point in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.  In no arm did more than three percent of individuals refuse loans subsequent to the survey, and neither these rates nor the rate of survey response are different across arms.  Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.

@@

\paragraph{Other costs.} We have shown that forcing borrowers to take the monthly payment contract significantly reduces financial cost. Although the paper focuses on financial cost, we consider three additional costs here. First, We include the cost of going to the branch. This includes the self-reported transport cost (most use public transport), as well as the opportunity cost of time. To err on the conservative side, we subtract a whole day's minimum wage the day of the visit, instead of just the wage corresponding to a couple of hours. Second, we consider a rough proxy of the value of liquidity they lose by paying earlier. We act as if each payment they make comes from an additional loan they take, which incurs interest at the same rate as Lender P's loan (7\% per month). So far we have valued the collateral at the gold value appraised by the lender, but the piece may be worth more to the borrower than its gold value. 
For many of them the pawned jewelry has sentimental value as well. This is reflected in the subjective valuation they reported in the survey\footnote{The minimum peso amount at which they would sell the piece.} which is \hl{XXX\%} higher on average. Our third extra cost considers this higher value.

Table \ref{table_robustness_fc} shows results. We present results

Columns (1) and (6) replicate our previous results for comparability. Columns (2) and (7) of Table \ref{table_robustness_fc} use the subjective value of the pawn reported by the borrower rather than its appraised value. Columns (3) and (8) adjust for self-reported transport costs from the individual survey plus an entire day's wage, multiplied by the number of individual visits\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents.}.
Although adding a whole day's wage almost certainly exaggerates the travel costs associated with commitment contracts, we still find that forced commitment reduces both financial costs and APR. 
Columns (4) and (9) adjust for both travel costs and use the subjective rather than appraised value of the pawn. Finally, columns (5) and (10) remove saved interest payments from the calculation of the benefits. The rationale is that forcing borrowers to pay earlier reduces their  liquidity, and they may need to borrow. We assume they borrow at the same interest rate. Thus considering other loans, they may not be paying less interest. The exercises in Table \ref{table_robustness_fc} show that results are quite robust to the inclusion and exclusion of components of benefits and costs.

@@

\todo[inline]{``fully adjusted'' in the table removes interest payments from the cost measure. Not totally clear what this exercise tells us. Overall, the point of the table is to remove alternative explanations one-by-one.  (I added a paragraph now to make this clearer, ES)}

@@

\paragraph{Repeat Pawns.}
%Another way to push the analysis towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.  We consider this outcome in Table \ref{repeat_loans}. We can first ask whether the individual ever takes a loan after the initial study loan, an analysis which is simply experimental.  
Table \ref{repeat_loans} explores the effects of treatment on future pawning behavior.
Column (1) shows that participants assigned to the the forced arm are 6.7\% more likely to be repeat clients.
Those in the choice arm are 4\% more likely to pawn again and is not statistically distinct from zero.  While this appears to be \emph{prima facie} evidence of greater satisfaction, the interpretation is complicated by the fact that monthly payments may themselves trigger more borrowing to pay them. This is unlikely to be the case given that the effect on re-pawning comes after 90 days (during the period of contract demanded payments) and not before  (see columns 2 and 3). Column 4 focuses on the (endogenous) subsample of those recovering their pawn in both arms of the experiment. This means that both have the pawn to re-pawn and also that the liquidity demands from the monthly contract are not longer binding as the contract has been terminated. Twice as many choose to pawn again in the commitment contract (column 4).

@@

The window of time during which we were able to observe borrower behavior was limited in each branch, meaning that there were loans that we do not see completed (particularly those pawns that were rolled over for one or two further 90-day spells).  Overall, XX\% of all experimental loans are censored, meaning that they neither default nor repay within the observation window.  In the prior analysis we handle this issue by using outcomes such as `did not default' which are defined even when we do not observe the completion of the loan, and only considering costs that we observe directly.  We have also showed, however, that one effect of the forcing arm is to accelerate repayment, meaning that it is less likely for loans in this arm to be censored.  This issue is illustrated in Figure \ref{survival_graph}, which shows the CDF of loan completion (Panel (a)) and loan recovery (Panel (b)) by the number of days since first pawn.  Two features of these graphs are salient for our analysis.  The first is the extent to which loan outcomes are observed more quickly in the forcing arm.  This is primarily due to the the substantially higher rate of repayment of Forced Commitment loans at 120 days (~15 pp higher than the other arms).  The second is the very low rate at which loans are recovered in any arm after 120 days.  In the 180 day window after the second rollover period we see a further ~10 percent of loans repaid in all arms, but these loans are largely dormant, suggesting that many of the censored loans will in fact be defaulted upon.

@@

The results from Section \ref{experiment} show that commitment \emph{works}: clients who were assigned to the forced commitment arm experienced substantially lower financial costs on average.
In spite of this, given the opportunity, only 11\% of borrowers chose commitment. 
If the effect of commitment were homogeneous, this would be enough to conclude that the \hl{89\%} who did not choose it would have been financially better-off if they had.
In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with individual rationality. 
Following the methodology of \cite{chernozhukov2018generic} we test and reject the null hypothesis of homogeneous treatment effects \hl{P-value = XXX}.\footnote{See Appendix \hl{???} for details.} 
Indeed, the effect of commitment varies considerably across individuals. 
So do the 89\% who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake? 
We now present a range of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
%Taken together, they cast considerable doubt on the notion of ``selection on gains,'' as embodied in the traditional Roy model. 
While we find evidence of substantial treatment effect heterogeneity, most borrowers would experience lower financial costs under a commitment contract. 
Among other results, we show that the average effect of commitment for the \emph{untreated}, those who would not voluntarily choose commitment, is large and negative. 
%In an important sense the ``wrong'' people are choosing commitment.

@@

To understand the relationship between choice and heterogeneous treatment effects, it is important to be precise about the potential outcomes in our empirical setting.
Let $Z_i \in \{0, 1, 2\}$ denote the treatment arm to which to participant $i$ was assigned: $Z_i = 0$ denotes the forced no-commitment arm, $Z_i = 1$ denotes the forced commitment arm, and $Z_i = 2$ denotes the choice arm. 
Now let $D_i$ be the treatment that participant $i$ actually \emph{received}, where $D_i = 0$ denotes no-commitment and $D_i = 1$ denotes commitment. 
By design, our experiment features perfect compliance in the $Z_i = 0$ and $Z_i = 1$ arms. 
It is only in the $Z_i = 2$ arm that participants are free to choose between alternative contracts. 
Let $C_i \in \{0, 1 \}$ denote a participant's ``choice type.'' If $C_i = 1$ then participant $i$ \emph{would choose commitment}, given the choice; if $C_i = 0$ she would not. 
Whereas a participant's choice type $C_i$ is only observed if she is allocated to the choice arm ($Z_i = 2$), her treatment $D_i$ and experimental arm $Z_i$ are always observed. 
Given the design of our experiment, these quantities are related by
\begin{equation}
D_i = \mathbbm{1}(Z_i \neq 2) Z_i + \mathbbm{1}(Z_i = 2) C_i.
\label{eq:potentialTreatments}
\end{equation}

We maintain the stable unit treatment value assumption (SUTVA) throughout. 
This means that participant $i$'s outcomes depend only on her \emph{own} values of $Z_i$ and $D_i$, not those of any other person in the experiment: there are no \emph{spillovers}. 
Under this assumption, a fully general model for the potential outcomes in our experiment would take the form $Y_i(d, z)$ for $d\in \{0,1\}$ and $z \in \{0, 1, 2\}$, allowing participant $i$'s potential outcome to depend \emph{both} on the treatment she actually receives, $D_i$, and the experimental arm to which she is assigned, $Z_i$. 
This model is too general, however, to identify meaningful causal effects. 
Accordingly, we impose the following standard exclusion restriction:
\begin{equation}
Y_i(d=0, z=0) = Y_i(d=0, z=2) \equiv Y_{i0}, \quad
Y_i(d=1, z=1) = Y_i(d=1, z=2) \equiv Y_{i1}.
\label{eq:exclusion}
\end{equation}
\eqref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment. Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, this nothing more than the usual IV exclusion restriction.\footnote{\cite{chamberlain2011bayesian} uses an identical assumption to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} \eqref{eq:exclusion} is plausible in our empirical setting and has testable implications that we fail to reject: see Appendix \hl{???} for details. Under \eqref{eq:exclusion}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to 
%\todo[inline]{Issac: add a section \ref{bound_tot_tut_appendix} to the appendix and drop in the results for the Huber \& Mellace stuff; Frank: follow-up and draft that section of the appendix.}
\begin{equation}
    Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].
\label{eq:potentialOutcomes}
\end{equation}

\eqref{eq:potentialOutcomes} is the key to understanding the results that follows. 
By randomly assigning $Z_i=0$ and $Z_i = 1$, our experiment identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ in the population as a whole. 
By randomly assigning $Z_i=2$, it likewise identifies the share of people with $C_i = 1$ (the treated), the distribution of $Y_{i1}$ for these individuals, and the distribution of $Y_{i0}$ for those with $C_i = 0$ (the untreated). 
Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, our design also identifies the corresponding \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$. 
%These distributions are the ingredients that we use below to explore the importance of paternalism.

@@

\subsection{Bounding the Distribution of Treatment Effects}

As seen above in Section \ref{experiment}, the average treatment effect of forced commitment is economically and statistically significant. 
Using the notation of Section \ref{sec:potentialOutcomes}, our estimate of $\mathbbm{E}[Y_{i1} - Y_{i0}]$ is \emph{negative}: commitment lowers financial costs overall. 
But this is only an average effect.
The ATE could still be negative if the individual treatment effects $\Delta_i = Y_{i1} - Y_{i0}$ are zero or positive for most people in the experiment.
Perhaps commitment is extremely helpful for a small minority of borrowers, and slightly harmful for everyone else.
Can this explanation rationalize the very low take-up rate of commitment in the choice arm (11\%) along with the ATE of commitment estimated from the forced arm? 
We could easily answer this question if the distribution $F_\Delta$ of individual treatment effects $\Delta_i$ were known: simply calculate $\mathbbm{P}(\Delta_i < 0)$.
But because we can never observe both $Y_{i0}$ and $Y_{i1}$ for the same person, $F_\Delta$ cannot be identified. 
It can, however, be bounded. 
Using these bounds, we now show that more than 11\% of individual borrowers benefit from commitment.

As explained above, our experimental design identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$, call them $F_0$ and $F_1$.
Now, define the functions $\underline{F}$ and $\overline{F}$ as follows:
\[
\underline{F}(\delta) \equiv \max \left\{0, \sup_y F_1(y) - F_0(y - \delta)  \right\}, \quad
\overline{F}(\delta) \equiv 1 + \min \left\{0, \inf_y F_1(y) - F_0(y-\delta) \right\}.
\]
Since $F_0$ and $F_1$ are point identified, so are $\underline{F}$ and $\overline{F}$.
\cite{fan2010sharp} show that the sharp (best possible) pointwise bounds for $F_\Delta$ are given by $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$
These bounds are simple to compute, and can be surprisingly informative. 
Here we use them to bound the fraction of borrowers who benefit from commitment. 
Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is \hl{\emph{negative}}, i.e.\ $F_\Delta(0)$. 
To construct the sharp bounds for this quantity, we simply substitute $\delta = 0$ into the preceding equations and estimate $F_0$ and $F_1$ using their empirical analogues constructed from the forced commitment and forced no-commitment arms of the experiment.

\todo[inline]{Issac: add in the confidence interval at $\delta = 0$ along with the figure \ref{fan_park_bounds}; Frank follow-up to add 1-2 sentences discussing the results. Presumably we find that $F_\Delta(0) > 0.11$ this means that at least some people who choose not to commit \emph{must} be making a mistake, although we don't know who they are and this doesn't tell us how large the mistake is.}

An alternative way of presenting the \cite{fan2010sharp} bounds is in terms of quantiles of the distribution of $\Delta$. Let $0 < q < 1$, and define $Q_0, Q_1, Q$ to be the quantile functions corresponding to $F_0, F_1$ and $F_\Delta$.\footnote{In other words, $Q_0(q) \equiv \inf \{x | F(x) \geq q\}$ and so on.} Then the sharp bound for $Q_\Delta(q)$ is given by $\underline{Q}(q) \leq Q(q) \leq \overline{Q}(q)$ where
\[
\overline{Q}(q) \equiv \inf_{u \in [q,1]} [Q_1(u) - Q_0(u - q)], \quad
\underline{Q}(q) \equiv \sup_{u\in [0,q]} [Q_1(u) - Q_0(1 + u - q)]
\]
By substituting $q = 0.11$, these expressions allow us to bound the 11th percentile of the distribution of $\Delta$. Under a stylized Roy model in which borrowers with the largest (negative) treatment effects choose commitment, $Q(0.11)$ equals the treatment effect for the borrower at the margin of indifference between choosing commitment.

\todo[inline]{Issac: add the interval for $Q(0.11)$. Maybe we don't need a second figure with the confidence bands for the whole quantile function. Frank: add a sentence or two discussing the results. Presumably the aforementioned quantile is indeed negative and fairly large.}

Taken together, these bounds show that at least some borrowers who would benefit from commitment \emph{do not choose it} when offered.

>>>>

\subsection{Experimental Integrity}
\label{sec:integrity}

\paragraph{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results. The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter.  If this occurred it would introduce a self-selection dimension which would still reflect the overall impact of a treatment for the lender's portfolio but would no longer deliver \textit{ceteris paribus} effects of treatments on individual borrowers.  Narrative reports and the way the treatment was implemented make us believe that selection into treatment is unlikely.\footnote{Potential clients did not know that different days could have different contracts. If they asked, appraisers said that whatever was offered on that day was the only available contract for an undetermined length of time. Anecdotally, appraisers told us that they did not think refusals differed across arms, and our enumerators informed us that potential clients rarely left the branch without pawning. Lender P also never complained to us that our different treatments were hurting sales.} If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms.  To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day. The \hl{first} row of Table \ref{attrition_table} shows there is no difference between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.\footnote{The Choice arm appears to have a somewhat larger number of borrowers than the Control arm (p-value=\hl{XXX}), but we cannot reject equality with the Forced Commitment arm (p-value=\hl{XXX}), or across all arms (p-value=\hl{XXX}).}  The second row makes the same point in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.  In no arm did more than three percent of individuals refuse loans subsequent to the survey, and neither these rates nor the rate of survey response are different across arms.  Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.

@@

\paragraph{Other costs.} We have shown that forcing borrowers to take the monthly payment contract significantly reduces financial cost. Although the paper focuses on financial cost, we consider three additional costs here. First, We include the cost of going to the branch. This includes the self-reported transport cost (most use public transport), as well as the opportunity cost of time. To err on the conservative side, we subtract a whole day's minimum wage the day of the visit, instead of just the wage corresponding to a couple of hours. Second, we consider a rough proxy of the value of liquidity they lose by paying earlier. We act as if each payment they make comes from an additional loan they take, which incurs interest at the same rate as Lender P's loan (7\% per month). So far we have valued the collateral at the gold value appraised by the lender, but the piece may be worth more to the borrower than its gold value.  For many of them the pawned jewelry has sentimental value as well. This is reflected in the subjective valuation they reported in the survey which is \hl{XXX\%} higher on average. Our third extra cost considers this higher value.

Table \ref{table_robustness_fc} shows results. Panel A reports financial cost in pesos, while Panel B shows APR. Columns (1) and (6) replicate our previous results for comparability. Columns (2) and (7) of Table \ref{table_robustness_fc} use the subjective value of the pawn reported by the borrower rather than its appraised value. Columns (3) and (8) adjust for self-reported transport costs per visit plus an entire day's wage, both multiplied by the number of individual visits\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents of the respective branch.}. Columns (4) and (9) adjust for our measure of liquidity cost. Finally columns (5) and (10) include all three changes together. The main takeaway from the table is that results are quite robust to including a much expanded measure of costs.

%Although adding a whole day's wage almost certainly exaggerates the travel costs associated with commitment contracts, we still find that forced commitment reduces both financial costs and APR. Columns (4) and (9) adjust for both travel costs and use the subjective rather than appraised value of the pawn. Finally, columns (5) and (10) remove saved interest payments from the calculation of the benefits. The rationale is that forcing borrowers to pay earlier reduces their liquidity, and they may need to borrow. We assume they borrow at the same interest rate. Thus considering other loans, they may not be paying less interest. The exercises in Table \ref{table_robustness_fc} show that results are quite robust to the inclusion and exclusion of components of benefits and costs.

@@

@@

\paragraph{Repeat Pawns.}
%Another way to push the analysis towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.  We consider this outcome in Table \ref{repeat_loans}. We can first ask whether the individual ever takes a loan after the initial study loan, an analysis which is simply experimental.  
Table \ref{repeat_loans} explores the effects of treatment on future pawning behavior.
Column (1) shows that participants assigned to the the forced arm are 6.7\% more likely to be repeat clients. %Those in the choice arm are 4\% more likely to pawn again and is not statistically distinct from zero. 
While this appears to be \emph{prima facie} evidence of greater satisfaction, the interpretation is complicated by the fact that monthly payments may themselves trigger more borrowing to pay them. This is unlikely to be the case given that the effect on re-pawning comes after 90 days (during the period of contract demanded payments) and not before  (see columns 2 and 3). Column 3 only considers new loans which use different collateral from that of the initial one. We do this to foreclose the explanation that those in the Forced arm repeat more because they are more likely to have collateral, as they recover the collateral of the first loan more often.  Column 5 focuses on the (endogenous) subsample of those recovering their pawn in both arms of the experiment. This means that both have the pawn to re-pawn and also that the liquidity demands from the monthly contract are not longer binding as the contract has been closed. We find that the difference between the Forcing contract and the status quo is even larger in this subsample, with the former having 11pp higher likelihood of being a repeat client during our sample period.

@@

The window of time during which we were able to observe borrower behavior was limited in each branch, meaning that there were loans that we do not see completed (particularly those pawns that were rolled over for one or two further 90-day spells).  Overall, \hl{XX\%} of all experimental loans are censored, meaning that they neither default nor repay within the observation window.  In the prior analysis we handle this issue by using outcomes such as `did not default' which are defined even when we do not observe the completion of the loan, and only considering costs that we observe directly.  We have also showed, however, that one effect of the forcing arm is to accelerate repayment, meaning that it is less likely for loans in this arm to be censored.  This issue is illustrated in Figure \ref{survival_graph}, which shows the CDF of loan completion (Panel (a)) and loan recovery (Panel (b)) by the number of days since first pawn.  Two features of these graphs are salient for our analysis.  The first is the extent to which loan outcomes are observed more quickly in the forcing arm.  This is primarily due to the the substantially higher rate of repayment of Forced Commitment loans at 120 days (~15 pp higher than the other arms).  The second is the very low rate at which loans are recovered in any arm after 120 days.  In the 180 day window after the second rollover period we see a further ~10 percent of loans repaid in all arms, but these loans are largely dormant, suggesting that many of the censored loans will in fact be defaulted upon.

@@

The results from Section \ref{experiment} show that commitment \emph{works}: clients who were assigned to the forced commitment arm experienced substantially lower financial costs on average.
In spite of this, given the opportunity, only \hl{11\%} of borrowers chose commitment. 
If the effect of commitment were homogeneous, this would be enough to conclude that the \hl{89\%} who did not choose it would have been financially better-off if they had.
In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with individual rationality.
The borrowers who did not choose commitment could simply be those who don't need it. 
Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: Appendix \ref{append:chernozhukov} tests and rejects the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}.
So the question remains: do the \hl{89\%} who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake? 
In this section we now present a range of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
Despite substantial treatment effect heterogeneity, most borrowers would experience lower financial costs under a commitment contract. 
Indeed, commitment lowers average financial costs even for the subset of borrowers who would \emph{not} choose to commit voluntarily.
To simplify the exposition in this and all sections that follow, we re-define all outcome variables so that \emph{beneficial} treatment effects are \emph{positive}. Using this convention, a positive treatment effect of commitment on financial cost, for example, reflects the average cost \emph{savings} caused by commitment.

@@

To understand the relationship between choice and heterogeneous treatment effects, it is important to be precise about the potential outcomes in our empirical setting.
Let $Z_i \in \{0, 1, 2\}$ denote the treatment arm to which to participant $i$ was assigned: $Z_i = 0$ denotes the forced no-commitment arm, $Z_i = 1$ denotes the forced commitment arm, and $Z_i = 2$ denotes the choice arm. 
Now let $D_i$ be the treatment that participant $i$ actually \emph{received}, where $D_i = 0$ denotes no-commitment and $D_i = 1$ denotes commitment. 
We assume perfect compliance in the $Z_i = 0$ and $Z_i = 1$ arms.\footnote{For more discussion on this point, see Section \ref{sec:integrity} above.}
It is only in the $Z_i = 2$ arm that participants are free to choose between alternative contracts. 
Let $C_i \in \{0, 1 \}$ denote a participant's ``choice type.'' If $C_i = 1$ then participant $i$ \emph{would choose commitment}, given the option; if $C_i = 0$ she would not. 
As shorthand, we call borrowers with $C_i = 1$ ``choosers'' and those with $C_i = 0$ ``non-choosers.''
Whereas a participant's choice type $C_i$ is only observed if she is allocated to the choice arm ($Z_i = 2$), her treatment $D_i$ and experimental arm $Z_i$ are always observed. 
Given the design of our experiment, these quantities are related by
\begin{equation}
D_i = \mathbbm{1}(Z_i \neq 2) Z_i + \mathbbm{1}(Z_i = 2) C_i.
\label{eq:potentialTreatments}
\end{equation}

We maintain the stable unit treatment value assumption (SUTVA) throughout. 
This means that borrower $i$'s outcomes depend only on her \emph{own} values of $Z_i$ and $D_i$, not those of any other person in the experiment: there are no \emph{spillovers}. 
Under this assumption, a fully general model for the potential outcomes in our experiment would take the form $Y_i(d, z)$ for $d\in \{0,1\}$ and $z \in \{0, 1, 2\}$, allowing participant $i$'s potential outcome to depend \emph{both} on the treatment she actually receives, $D_i$, and the experimental arm to which she is assigned, $Z_i$. 
This model is too general, however, to identify meaningful causal effects. 
For this reason, we impose two exclusion restrictions.
Before stating them, we first define some additional notation.
In particular, because any anyone with $Z_i = 0$ has $D_i = 0$ under our experimental design, we abbreviate the potential outcome $Y_i(d=0,z=0)$ as $Y_{i0}$. 
Similarly, as anyone with $Z_i = 1$ has $D_i = 1$, we abbreviate $Y_i(d=1,z=1)$ as $Y_{i1}$. 
Our first exclusion restriction is relevant only for non-choosers, individuals with $C_i = 0$, because they are the only borrowers for whom $D_i = 0$ when $Z_i = 2$.
We assume that
\begin{equation}
Y_i(d=0,z=2) = Y_i(d=0,z=0) \equiv Y_{i0}.
\label{eq:exclusion0}
\end{equation}
Equation \ref{eq:exclusion0} implies that every non-chooser experiences the same potential outcome when assigned to the control arm as when assigned to the choice arm. 
Our second exclusion is relevant only for choosers, individuals $C_i =1$, because they are the only borrowers for whom $D_i = 1$ when $Z_i = 2$.
We assume that 
\begin{equation}
Y_i(d=1,z=2) = Y_i(d=1,z=1)\equiv Y_{i1}.
\label{eq:exclusion1}
\end{equation}
Equation \ref{eq:exclusion1} implies that every chooser experiences the same potential outcome when assigned to the treatment arm as when assigned to the choice arm. 
Mathematically \eqref{eq:exclusion0} and \eqref{eq:exclusion0} have the same structure as the standard LATE exclusion restriction that $Y_i(d,z)$ depends only on $d$, not on $z$. 
Substantively, however, they are slightly different as there is no analogue of the ``chosen'' versus ``forced'' treatment distinction in the usual LATE setting.\footnote{See \cite{chamberlain2011bayesian}, who uses an assumption very similar to our exclusion restrictions to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} 
Both \eqref{eq:exclusion0} and \eqref{eq:exclusion1} are plausible in our empirical setting. 
Moreover, each has testable implications that we fail to reject: see Appendix \ref{append:exclusion} for details. Under \eqref{eq:exclusion}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to  
\begin{equation}
    Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].
\label{eq:potentialOutcomes}
\end{equation}
%\todo[inline]{Fix labels!}
%Accordingly, we impose the following standard exclusion restriction:
%\begin{equation}
%Y_i(d=0, z=0) = Y_i(d=0, z=2) \equiv Y_{i0}, \quad
%Y_i(d=1, z=1) = Y_i(d=1, z=2) \equiv Y_{i1}.
%\label{eq:exclusion}
%\end{equation}
%Equation \ref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment. Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, \eqref{eq:exclusion} amounts to the usual IV exclusion restriction.
%
%\todo[inline]{END Fix labels!}
Equation \ref{eq:potentialOutcomes} is the key to understanding the results that follows. 
By randomly assigning $Z_i=0$ and $Z_i = 1$, our experiment identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ in the population as a whole. 
By randomly assigning $Z_i=2$, it likewise identifies the share of choosers ($C_i = 1$), the distribution of $Y_{i1}$ for choosers, and the distribution of $Y_{i0}$ for non-choosers ($C_i = 0$).
Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, our design also identifies the corresponding \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$. 
%These distributions are the ingredients that we use below to explore the importance of paternalism.

@@

\subsection{Bounding the Distribution of Treatment Effects}
\todo[inline]{Unless I'm missing something obvious, this section does not rely on the exclusion restriction. We should think of a way to highlight this.}
As seen above in Section \ref{experiment}, the average treatment effect of forced commitment is economically and statistically significant. 
Using the notation of Section \ref{sec:potentialOutcomes}, our estimate of $\mathbbm{E}[Y_{i1} - Y_{i0}]$ is positive: commitment lowers financial costs overall.\footnote{Recall from above that in this section we define all outcome variables so that beneficial treatment effects are \emph{positive}.}
But this is only an average effect.
The ATE could still be negative if the individual treatment effects $\Delta_i = Y_{i1} - Y_{i0}$ are zero or positive for most people in the experiment.
Perhaps commitment is extremely helpful for a small minority of borrowers, and slightly harmful for everyone else.
Can this explanation rationalize the very low take-up rate of commitment in the choice arm (\hl{11\%}) along with the ATE of commitment estimated from the forced arm? 
We could easily answer this question if the distribution $F_\Delta$ of individual treatment effects $\Delta_i$ were known: simply calculate $\mathbbm{P}(\Delta_i < 0)$.
But because we can never observe both $Y_{i0}$ and $Y_{i1}$ for the same person, $F_\Delta$ cannot be identified. 
It can, however, be bounded. 
Using these bounds, we now show that more than \hl{11\%} of individual borrowers benefit from commitment.

As explained above, our experimental design identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$, call them $F_0$ and $F_1$.
Now, define the functions $\underline{F}$ and $\overline{F}$ as follows:
\[
\underline{F}(\delta) \equiv \max \left\{0, \sup_y F_1(y) - F_0(y - \delta)  \right\}, \quad
\overline{F}(\delta) \equiv 1 + \min \left\{0, \inf_y F_1(y) - F_0(y-\delta) \right\}.
\]
Since $F_0$ and $F_1$ are point identified, so are $\underline{F}$ and $\overline{F}$.
\cite{fan2010sharp} show that the sharp (best possible) pointwise bounds for $F_\Delta$ are given by $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$
These bounds are simple to compute, and can be surprisingly informative. 
Here we use them to bound the fraction of borrowers who benefit from commitment. 
Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is \emph{positive}, i.e.\ $1 - F_\Delta(0)$. 
To construct the sharp bounds for this quantity, we simply substitute $\delta = 0$ into the preceding equations and estimate $F_0$ and $F_1$ using their empirical analogues constructed from the forced commitment and forced no-commitment arms of the experiment.

Figure \ref{fig:FanPark} plots the sharp bounds for $F_{\delta}$ based on the APR outcome defined above in Section \ref{costs}. Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are \hl{XXXX} and \hl{XXXX} respectively, with associated 95\% confidence intervals of \hl{XXXX} and \hl{XXXX}.\footnote{Confidence intervals are constructed using \hl{XXXX} bootstrap. See \cite{fan2010sharp} for details.}
%\todo[inline]{Issac: add in the confidence interval at $\delta = 0$ along with the figure \ref{fan_park_bounds}. These need to be the results that do not use covariates and we need to be careful about the sign convention for our effects. Frank follow-up to add 1-2 sentences discussing the results. Presumably we find that $F_\Delta(0) > 0.11$ this means that at least some people who choose not to commit \emph{must} be making a mistake, although we don't know who they are and this doesn't tell us how large the mistake is.}
An alternative way of presenting the \cite{fan2010sharp} bounds is in terms of quantiles of the distribution of $\Delta$. Let $0 < q < 1$, and define $Q_0, Q_1, Q$ to be the quantile functions corresponding to $F_0, F_1$ and $F_\Delta$.\footnote{In other words, $Q_0(q) \equiv \inf \{x | F(x) \geq q\}$ and so on.} Then the sharp bound for $Q_\Delta(q)$ is given by $\underline{Q}(q) \leq Q(q) \leq \overline{Q}(q)$ where
\[
\overline{Q}(q) \equiv \inf_{u \in [q,1]} [Q_1(u) - Q_0(u - q)], \quad
\underline{Q}(q) \equiv \sup_{u\in [0,q]} [Q_1(u) - Q_0(1 + u - q)]
\]
By substituting $q = 0.11$, these expressions allow us to bound the 11th percentile of the distribution of $\Delta$. Under a stylized Roy model in which borrowers with the largest (negative) treatment effects choose commitment, $Q(0.11)$ equals the treatment effect for the borrower at the margin of indifference between choosing commitment. 
Our point estimates for the lower and upper bounds $\underline{Q}(0.11)$ and $\overline{Q}(0.11)$ are \hl{XXXX} and \hl{XXXX} with corresponding 95\% confidence intervals \hl{XXXX} and \hl{XXXX}.\footnote{Again, confidence intervals are constructed using \hl{XXXX} bootstrap as describe in \cite{fan2010sharp}.}
%\todo[inline]{Issac: add the interval for $Q(0.11)$. Again, this needs to be without covariates and we need to be careful about the sign convention for our effects. Maybe we don't need a second figure with the confidence bands for the whole quantile function. Frank: add a sentence or two discussing the results. Presumably the aforementioned quantile is indeed negative and fairly large.}
Both ways of presenting the bounds yield the same conclusion: at least some borrowers who would benefit from commitment \emph{do not choose it} when offered.
